---
title: "filter-for-names.Rmd"
output: html_document
---

Load data

```{r}
mydata <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
```

View the column names and verify that there is a column called `"Country.Region"`.

```{r}
View(colnames(mydata))
```

We see that columns can be identified by numbers and by strings. For example the column at index 2 is named "Country.Region". To extract this column, we can use the number (as we did before when we processed mydata)

```{r}
View(mydata[,2])
```

or we can use the name as in

```{r}
View(mydata[,"Country.Region"])
```

It seems that in `mydata[,X])` what we fill in for `X` can be either a number or a string. To let R know that `Country.Region` is a string we need to put it in double quotes.

By the way, instead of `View(mydata[,"Country.Region"])` we can also use

```{r}
View(mydata$"Country.Region")
```

but, apparently, the `$` notation only works for strings, not for numbers:

```{r}
View(mydata$2)
```

Surprisingly, we get a different (but still non-intended) result if we replace the `2` above by a variable that has value `2`:

```{r}
X <- 2
View(mydata$X)
```

Anyway, let us go back to the question of how to search and filter the data for a string such as "Germany":

```{r}
View(mydata[mydata[,"Country.Region"]=="Germany",])
```

Now you should see the row that has "Germany" in the column named "Country.Region". If you find that this looks horrible, I agree. Book this under boring-but-necessary. Like English spelling.

Finally, if we want to access a row by its name, which is a number for our current example data, we can find it using the `row.names()` function:

```{r}
View(row.names(mydata[mydata[,"Country.Region"]=="Germany",]))
```


We can use this now to improve our code. We can parameterise it, not by numbers that we have to look up in a table (and that can change over time), but by names of regions.

Here it is:

```{r}
    # User input
    region1_name <- "Austria"
    region2_name <- "Italy"
    range <- 15           
    region1_first <- 15   
    region2_first <- 35     
    population_ratio_region1_region2 <- 1.38

    # Automated processing
    region1 <- row.names(mydata[mydata[,"Country.Region"]==region1_name,])
    region2 <- row.names(mydata[mydata[,"Country.Region"]==region2_name,])

    region1_deaths <- mydata[region1,(ncol(mydata)-region1_first):(ncol(mydata)-region1_first+range)]
    region1_deaths <- gsub(",", "", region1_deaths)                     
    region1_deaths <- as.numeric(region1_deaths)                      
    plot(region1_deaths, col="black", main=paste(mydata[region1,2], "(black), ", mydata[region2,2],  "(red)"), xlab="days", ylab=paste(mydata[region1,2], "deaths"))   
    
    region2_deaths <- mydata[region2,(ncol(mydata)-region2_first):(ncol(mydata)-region2_first+range)]
    #View(mydata[region2,1:2])       
    region2_deaths <- gsub(",", "", region2_deaths)                   
    region2_deaths <- as.numeric(region2_deaths)                      
    lines(population_ratio_region1_region2*region2_deaths, col="red")   
```

The next improvement is to calculate the population ratio. First we import some data

```{r}
    data_countries_by_population <- read.csv(url("https://raw.githubusercontent.com/datasets/population/master/data/population.csv"))
```

```{r}
    dcp <- data_countries_by_population
```

We go now through the same steps as before:

```{r}
View(colnames(data_countries_by_population))
```

```{r}
View(dcp[,"Country.Name"])
```

```{r}
View(dcp[dcp[,"Country.Name"]==region1_name,])
```

Here something new shows up. We get a long list comprising years from approx 1961 go 2016. How do we select a year? 

```{r}
View(dcp[dcp[,"Country.Name"]==region1_name & dcp[,"Year"]==2015,])
```


```{r}
View(dcp[dcp[,"Country.Name"]==region1_name & dcp[,"Year"]==2015,])
```


```{r}
    View(row.names(dcp[dcp[,"Country.Name"]==region1_name & dcp[,"Year"]==2015,]))
```

And now the population:

```{r}
    View(dcp[dcp[,"Country.Name"]==region1_name & dcp[,"Year"]==2015,"Value"])
```

Now we can compute

```{r}
    pop1 <- dcp[dcp[,"Country.Name"]==region1_name & dcp[,"Year"]==2015,"Value"]
    pop2 <- dcp[dcp[,"Country.Name"]==region2_name & dcp[,"Year"]==2015,"Value"]
    population_ratio_region1_region2 <- pop1/pop2
```

Finally, putting all together

```{r}
    # User input
    region1 <- "Austria"
    region2 <- "Italy"
    range <- 15           
    region1_first <- 15   
    region2_first <- 35     

    # Automatically processed from here
    
    # Load coronavirus data from Johns Hopkins
    corona_data <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
    
    # Load population data
    population_data <- read.csv(url("https://raw.githubusercontent.com/datasets/population/master/data/population.csv"))
    
    # Compute population ratio of the twi regions
    pop1 <- dcp[dcp[,"Country.Name"]==region1 & dcp[,"Year"]==2015,"Value"]
    pop2 <- dcp[dcp[,"Country.Name"]==region2 & dcp[,"Year"]==2015,"Value"]
    population_ratio_region1_region2 <- pop1/pop2

    # Automated processing
    r1 <- row.names(mydata[mydata[,"Country.Region"]==region1,])
    r2 <- row.names(mydata[mydata[,"Country.Region"]==region2,])

    region1_deaths <- mydata[r1,(ncol(mydata)-region1_first):(ncol(mydata)-region1_first+range)]
    region1_deaths <- gsub(",", "", region1_deaths)                     
    region1_deaths <- as.numeric(region1_deaths)                      
    plot(region1_deaths, col="black", main=paste(mydata[r1,2], "(black), ", mydata[r2,2],  "(red)"), xlab="days", ylab=paste(mydata[region1,2], "deaths"))   
    
    region2_deaths <- mydata[r2,(ncol(mydata)-region2_first):(ncol(mydata)-region2_first+range)]
    #View(mydata[region2,1:2])       
    region2_deaths <- gsub(",", "", region2_deaths)                   
    region2_deaths <- as.numeric(region2_deaths)                      
    lines(population_ratio_region1_region2*region2_deaths, col="red")   

```



```{r}
    # User input
    region1     <- "US"             # Name of region1 in the corona_data table
    region1_pop <- "United States"  # Name of region1 in the population_data table
    region2 <- "Italy"
    region2_pop <- region2  # Name of region1 in the population_data table
    range <- 15           
    region1_first <- 15   
    region2_first <- 35     
    
    # Output: If the graphs match, the estimated lag is the `region1_first - region2_first`

    # Automatically processed from here
    state1 <- ""              # Column 1 of the corona_data table
    state2 <- ""              # Column 1 of the corona_data table
    
    # Load coronavirus data from Johns Hopkins
    corona_data <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
    
    # Load population data
    population_data <- read.csv(url("https://raw.githubusercontent.com/datasets/population/master/data/population.csv"))
    
    # Abbreviations
    cd <- corona_data
    pd <- population_data
    r1 <- row.names(cd[cd[,"Country.Region"]==region1 & cd[,"Province.State"]==state1,])
    r2 <- row.names(cd[cd[,"Country.Region"]==region2 & cd[,"Province.State"]==state1,])

    # Compute the population ratio of the two regions
    pop1 <- pd[pd[,"Country.Name"]==region1_pop & pd[,"Year"]==2015,"Value"]
    pop2 <- pd[pd[,"Country.Name"]==region2_pop & pd[,"Year"]==2015,"Value"]
    population_ratio_region1_region2 <- pop1/pop2

    # Uncomment for debugging
    # View(cd[r1,])
    # View(cd[r2,])
    # View(pd[pd[,"Country.Name"]==region1_pop & pd[,"Year"]==2015,]) 
    # View(pd[pd[,"Country.Name"]==region2_pop & pd[,"Year"]==2015,]) 

    region1_deaths <- cd[r1,(ncol(cd)-region1_first):(ncol(cd)-region1_first+range)]
    region1_deaths <- gsub(",", "", region1_deaths)                     
    region1_deaths <- as.numeric(region1_deaths)                      
    plot(region1_deaths, col="black", main=paste(cd[r1,2], "(black), ", cd[r2,2],  "(red)"), xlab="days", ylab=paste(cd[r1,2], "deaths"))   
    
    region2_deaths <- cd[r2,(ncol(cd)-region2_first):(ncol(cd)-region2_first+range)]
    #View(cd[region2,1:2])       
    region2_deaths <- gsub(",", "", region2_deaths)                   
    region2_deaths <- as.numeric(region2_deaths)                      
    lines(population_ratio_region1_region2*region2_deaths, col="red")   

```



