---
title: "Data Wrangling"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

## Data Wrangling

```{r, echo=FALSE}    
library(tidyverse)
library(lubridate)
```

**Exercise:** Rewrite the code under "Selecting and renaming columns" in the style of pipes.

```{r, echo=FALSE}    

deaths_df <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

last_column <- colnames(deaths_df)[ncol(deaths_df)]

deaths_df %>%
  select(-UID,-iso2,-iso3,-code3,-FIPS,-Country_Region,-Lat,-Long_,-Combined_Key) %>%
  rename(county=Admin2,state=Province_State,population=Population) ->
  deaths
```

**Exercise:** Add the states to the names of the counties in the plot. Hint: Add a new column to the table using mutate() and paste(). Then color wrt to the new column.

```{r}
### Filter and pivot counties, summarise the topmost deaths_per_million by date

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  mutate(county_state=paste(county,state)) %>%
  drop_na() %>%
  mutate(deaths_per_million=as.numeric(deaths)*as.numeric(population)/1000000) %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(100) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color=county_state)) 
```

**Exercise:** Remove New York from the data above and plot again.

```{r}
### Filter and pivot counties, summarise the topmost deaths_per_million by date (excluding New York)

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million=as.numeric(deaths)*as.numeric(population)/1000000) %>%
  filter(!county=="New York") %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(100) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color=county)) 
```

**Exercise:** Remove New York from the plot and draw again

```{r}
### Summarise deaths by state and date (excluding New York)

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million=as.numeric(deaths)*as.numeric(population)/1000000) %>%
  filter(!state=="New York") %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(100, deaths_per_million) %>%
  
  group_by(state,date) %>%
  summarise_at(vars(deaths),sum) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths,color=state)) 
```

**Exercise:** Remove New York from the plot and draw again

```{r}
### Summarise deaths_per_million by state and date

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million = as.numeric(deaths)*as.numeric(population)/1000000) %>%
  filter(!state=="New York") %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(150, deaths_per_million) %>%
  
  group_by(state,date) %>%
  summarise_at(vars(deaths_per_million),sum) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color=state)) 
```


