---
title: "Data Wrangling 2"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Open this file in Rstudio.

## Data Wrangling

```{r}    
library(tidyverse)
library(lubridate)

deaths_df <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

deaths_df %>%
  as_tibble() %>%
  select(-UID,-iso2,-iso3,-code3,-FIPS,-Country_Region,-Lat,-Long_,-Combined_Key) %>%
  rename(county=Admin2,state=Province_State,population=Population) %>%
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  mutate(population=as.numeric(population)) ->
deaths_tibble
```

```{r}
deaths_tibble %>%
  pivot_longer(c(`1/22/20`:ncol(.)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  mutate(deaths_per_million = round(as.numeric(deaths)/population*1000000)) ->
deaths
```

To compute the total population of all counties listed in the table, it is better not pivot first. To understand why compare the pivoted table `deaths` and the not-pivted table `deaths_tibble`.

```{r}
deaths_tibble %>%
  group_by(state) %>%
  summarise(state_pop = sum(population)) ->
state_populations

state_populations %>%
  summarise(us_pop = sum(state_pop)) ->
us_population
```

**Exercise:** What result do you get for `us_population` if you replace `deaths_tibble` by `deaths` in the above computation? Can you explain the difference?

```{r}
deaths %>% 
  subset(date > as.Date("2020-03-15")) %>%
  group_by(state,date) %>%
  summarise_at(vars(deaths),sum) %>%
  ungroup() %>%
  inner_join(state_populations, by = c("state" = "state")) %>%
  mutate(deaths_per_million = round(deaths/state_pop*1000000)) ->
state_deaths_per_million

state_deaths_per_million %>%
  arrange(desc(deaths_per_million)) %>%
  distinct(state) %>%
  slice(1:10) ->
sliced_states

state_deaths_per_million %>%
  inner_join(sliced_states, by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color = state))
```

A grouping doesn't change how the data looks (apart from the order in which the data is listed). It changes how it acts with the other "verbs" such as `summarise` and `filter`. Sometimes it can have surprising consequences. For example, the top_n() is affected by the group_by() quite far above in case we do not follow the group_by() by an ungroup().

**Exercise:** Uncomment the `View` afer `top_n(10)` and comment out the `ungroup()` above. Observe how this changes the table resulting from `top_n(10)`.



```{r} THIS DOESNT WORK ... JUST A LEFTOVER FROM THE ABOVE ...
deaths %>% 
  subset(date > as.Date("2020-03-15")) %>%
  mutate(deaths_per_million = round(deaths/state_pop*1000000)) %>%
  group_by(state,date) %>%
  summarise_at(vars(deaths,deaths_per_milion),sum) %>%
    View

  inner_join(state_populations, by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million))
```


**New References** for Lesson 2:

- [distinct()](https://dplyr.tidyverse.org/reference/distinct.html)
- [inner_join()](https://dplyr.tidyverse.org/reference/join.html)
- [arrange()](https://dplyr.tidyverse.org/reference/arrange.html)
- [slice()](https://dplyr.tidyverse.org/reference/slice.html)

**References** from Lesson 1:

- [%>%](https://magrittr.tidyverse.org/)
- [filter()](https://r4ds.had.co.nz/transform.html#filter-rows-with-filter)
- [geom_line()](http://www.sthda.com/english/wiki/ggplot2-line-plot-quick-start-guide-r-software-and-data-visualization)
- [ggplot()](https://r4ds.had.co.nz/data-visualisation.html#creating-a-ggplot)
- [group_by()](https://dplyr.tidyverse.org/reference/group_by.html)
- [mdy(),lubridate](https://lubridate.tidyverse.org/)
- [mutate()](https://dplyr.tidyverse.org/reference/mutate.html), 
- [ncol(.)](https://magrittr.tidyverse.org/)
- [pivot_longer()](https://r4ds.had.co.nz/tidy-data.html#pivoting)
- [select()](https://r4ds.had.co.nz/transform.html#select)
- [summarise_at()](https://suzan.rbind.io/2018/04/dplyr-tutorial-4/#summarise-at)
- [top_n()](https://dplyr.tidyverse.org/reference/top_n.html)
- [vertical labels on the x-axis](https://stackoverflow.com/a/1331400/4600290)

**Further References:** Suzan Baert's Tutorial:
  
- [Part 1: select columns](https://suzan.rbind.io/2018/01/dplyr-tutorial-1/)
- [Part 2: transform columns](https://suzan.rbind.io/2018/02/dplyr-tutorial-2/)
- [Part 3: filter rows](https://suzan.rbind.io/2018/02/dplyr-tutorial-3/)
- [Part 4: summarize and slice data](https://suzan.rbind.io/2018/04/dplyr-tutorial-4/)

