---
title: "Data Wrangling"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

Open this file in Rstudio.

## Data Wrangling

```{r}    
library(tidyverse)
library(lubridate)
```

### Selecting and renaming columns

```{r}    

deaths_df <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

deaths <- as_tibble(deaths_df)

### Selecting

deaths <- select(deaths,-UID,-iso2,-iso3,-code3,-FIPS,-Country_Region,-Lat,-Long_,-Combined_Key)

### Rename column names

deaths <- rename(deaths,county=Admin2,state=Province_State,population=Population)
```

### Filter and pivot counties, summarise the topmost deaths_per_million by date

```{r}

#### Filter out all rows that are not counties

deaths_counties <- filter(deaths, !(county=="") & !(county=="Unassigned") & !grepl("Out of",county))

#### Pivot the date columns to get a tidy table

deaths_counties_pivoted <- pivot_longer(deaths_counties,c(`1/22/20`:ncol(deaths_counties)),names_to="date",values_to="deaths")

#### Convert dates from strings to dates

deaths_counties_pivoted <- mutate(deaths_counties_pivoted,date=mdy(date))

#### Eliminate rows with undefined cells (not needed here)

deaths_counties_pivoted <- drop_na(deaths_counties_pivoted)

#### Add a column "deaths_per_million"

deaths_counties_pivoted <- mutate(deaths_counties_pivoted,deaths_per_million=as.numeric(deaths)/as.numeric(population)*1000000)

#### Select dates after March 1

deaths_counties_pivoted <- subset(deaths_counties_pivoted, date > as.Date("2020-03-01"))

#### Select counties with the most ...

deaths_counties_pivoted <- top_n(deaths_counties_pivoted, 150, deaths_per_million)

#### Plot

ggplot(deaths_counties_pivoted) + geom_line(mapping = aes(x = date, y = deaths_per_million,color=county)) 
```

The code above is a bit lengthy and contains unncessary clutter, in particular the variable names. Note how we have `deaths`, `deaths_counties`, `deaths_counties_pivoted` and always need to think about whether to reuse the same variable name or whether to choose a fresh one. This inconvenience has a deeper signficance, it indicates that we are not operating on the right level of abstraction. Cudos to the inventors of R who are always striving for providing the right level of asbtraction to the practicioner. Here it is called pipes.

### Pipes

The code below is really exactly the same as the one above, just much more easy to write, read and maintain. Note how, with a bit of practice, each line of code matches up exactly with one data analysis step. 

```{r}
### Filter and pivot counties, summarise the topmost deaths_per_million by date

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:ncol(.)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million=as.numeric(deaths)/as.numeric(population)*1000000) %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(100, deaths_per_million) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color=county)) 
```

**Exercise:** Rewrite the code under "Selecting and renaming columns" in the style of pipes.

**Exercise:** Add the states to the names of the counties in the plot. Hint: Add a new column to the table using mutate() and paste(). Then color wrt to the new column.

**Exercise:** Remove New York from the data above and plot again.

```{r}
### Summarise deaths by state and date

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million=as.numeric(deaths)/as.numeric(population)*1000000) %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(200, deaths_per_million) %>%
  
  group_by(state,date) %>%
  summarise_at(vars(deaths),sum) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths,color=state)) 
```

**Exercise:** Remove New York from the plot and draw again

```{r}
### Summarise deaths_per_million by state and date

deaths %>% 
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million = as.numeric(deaths)/as.numeric(population)*1000000) %>%
  subset(date > as.Date("2020-03-01")) %>%
  top_n(150, deaths_per_million) %>%
  
  group_by(state,date) %>%
  summarise_at(vars(deaths_per_million),sum) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color=state)) 
```

**Exercise:** Remove New York from the plot and draw again

## Further Analysis of the table `time_series_covid19_deaths_US.csv`

```{r}
### Filter, pivot and plot territories

deaths %>%
  filter(county == "") %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million = as.numeric(deaths)/as.numeric(population)*1000000) %>%
  subset(date > as.Date("2020-03-01")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million,color=state)) 
```

```{r}
### Filter, pivot and plot territories (excluding Puerto Rico)

deaths %>%
  filter(county == "") %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  drop_na() %>%
  mutate(deaths_per_million = as.numeric(deaths)/as.numeric(population)*1000000) %>%
  subset(date > as.Date("2020-03-01")) %>%
  filter(!state == "Puerto Rico") %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths,color=state)) 
```

**Exercise:** Rewrite the code below using pipes

```{r}
### Filter, pivot  and plot "Unassigned"
deaths_us_unassigned <- filter(deaths, (county=="Unassigned"))
deaths_us_unassigned_pivoted <- pivot_longer(deaths_us_unassigned,c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths")
deaths_us_unassigned_pivoted <- mutate(deaths_us_unassigned_pivoted,date=mdy(date))
ggplot(data = deaths_us_unassigned_pivoted) + geom_point(mapping = aes(x = state, y = deaths)) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

**Exercise:** Correct the error in the code below

```{r}
### Filter, pivot and plot "Out of"
deaths_us_outof <- filter(deaths, grepl("Out of",county))
deaths_us_outof <- select(deaths_us_outof, -county)

deaths_us_outof_pivoted <- pivot_longer(deaths_us_outof,c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths")

deaths_us_outof_pivoted <- mutate(deaths_us_outof_pivoted,date=mdy(date))
window <- summarise_at(group_by(window,state),vars(deaths),sum)
ggplot(data = window) + geom_point(mapping = aes(x = state, y = deaths)) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

**References** I used to write this lesson:

- [%>%](https://magrittr.tidyverse.org/)
- [filter()](https://r4ds.had.co.nz/transform.html#filter-rows-with-filter)
- [geom_line()](http://www.sthda.com/english/wiki/ggplot2-line-plot-quick-start-guide-r-software-and-data-visualization)
- [ggplot()](https://r4ds.had.co.nz/data-visualisation.html#creating-a-ggplot)
- [group_by()](https://dplyr.tidyverse.org/reference/group_by.html)
- [mdy(),lubridate](https://lubridate.tidyverse.org/)
- [mutate()](https://dplyr.tidyverse.org/reference/mutate.html), 
- [ncol(.)](https://magrittr.tidyverse.org/)
- [pivot_longer()](https://r4ds.had.co.nz/tidy-data.html#pivoting)
- [select()](https://r4ds.had.co.nz/transform.html#select)
- [summarise_at()](https://suzan.rbind.io/2018/04/dplyr-tutorial-4/#summarise-at)
- [top_n()](https://dplyr.tidyverse.org/reference/top_n.html)
- [vertical labels on the x-axis](https://stackoverflow.com/a/1331400/4600290)

**Further References:** Suzan Baert's Tutorial:
  
- [Part 1: select columns](https://suzan.rbind.io/2018/01/dplyr-tutorial-1/)
- [Part 2: transform columns](https://suzan.rbind.io/2018/02/dplyr-tutorial-2/)
- [Part 3: filter rows](https://suzan.rbind.io/2018/02/dplyr-tutorial-3/)
- [Part 4: summarize and slice data](https://suzan.rbind.io/2018/04/dplyr-tutorial-4/)

