---
title: "Coronavirus "
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, echo=FALSE}
source("../src/covid-19_global.R")
```

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-South_Korea.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-South_Korea.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

## March 2

On March 2, Italy is 4 days behind South Korea and both countries seem on the same trajectory as far as cases are concerned.

```{r, echo=FALSE}
two_regions(what="cases",data=_global,region1="Italy",region2="Korea, South",region2_pop="Korea, Rep.", last_day="3/2/20",range=12,lag=4)
```

But already in the number of deaths there is a big difference apparent.

```{r}
two_regions(what="deaths",data=deaths_global,region1="Italy",region2="Korea, South",region2_pop="Korea, Rep.", last_day="3/2/20",range=12,lag=4)
```

## Latest plots

These trends have been continuing.

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Italy",region2="Korea, South",region2_pop="Korea, Rep.",range=50) 
```


```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Italy",region2="Korea, South",region2_pop="Korea, Rep.",range=50) 
```
