---
title: "Coronavirus in Brazil"
output: html_document
---

```{r, echo=FALSE}
source("../src/library3.R")
```

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Brazil.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Brazil.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

## March 19

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Brazil",region2="Italy",last_day="3/19/20",range=18,lag=25) 
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Brazil",region2="Italy",last_day="3/19/20",range=18,lag=26) 
```

## March 27

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Brazil",region2="Italy",last_day="3/27/20",lag=27)
```


```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Brazil",region2="Italy",last_day="3/27/20",lag=27)
```

## April 2

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Brazil",region2="Italy",last_day="4/2/20",lag=30)
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Brazil",region2="Italy",last_day="4/2/20",lag=29)
```
