---
title: "Coronavirus Los Angeles vs Italy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size = 1>
We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv). The program that produces the plots is available as [report-Los-Angeles.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Los-Angeles.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details. (In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
</font>

```{r, echo=FALSE}    
deaths_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

cases_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"),check.names = FALSE)

deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

source("../src/covid-19_US.R")
```

# Latest plots

I would expect that cities, being more densely populated, are worse affected than countries, but Los Angeles is on a flatter trajectory than Italy was 30 days ago when both had (corrected for population size) the same number of deaths:

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Los Angeles",province_state="California",region2="Italy",lag=30)
```

# April 7

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Los Angeles",province_state="California",region2="Italy",lag=25,last_day="4/7/20")
```

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Los Angeles",province_state="California",region2="Italy",lag=19,last_day="4/7/20")
```

# March 30

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Los Angeles",province_state="California",region2="Italy",lag=22,last_day="3/30/20")
```


```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Los Angeles",province_state="California",region2="Italy",lag=18,last_day="3/30/20")
```

