---
title: "Coronavirus "
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, echo=FALSE}
source("../src/covid-19_global.R")
```

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-US-South_Korea.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-US-South_Korea.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```


## Overview of coronavirus cases and deaths in South Korea

```{r, echo=FALSE}
one_region(what="cases",data=cases_global,region="Korea, South",range=60)
```

```{r, echo=FALSE}
one_region(what="deaths",data=deaths_global,region="Korea, South",range=60)
```

But already in the number of deaths there is a big difference apparent.

```{r}
two_regions(what="deaths",data=deaths_global,region1="Italy",region2="Korea, South",region2_pop="Korea, Rep.", last_day="3/2/20",range=12,lag=4)
```

## Comparison with the US

The comparison of case numbers suggests that South Korea was ahead of the US a month ago. But, crucially, South Korea was on a linear trajectory.

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="US",region1_pop="United States",region2="Korea, South",region2_pop="Korea, Rep.",range=60) 
```

On the other hand, a month ago the US was already on an expoenential trajectory, as can be seen by zooming into the data:

this picture would be bettr without South Korea ... apdapt one_region ...


```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="US",region1_pop="United States",region2="Korea, South",region2_pop="Korea, Rep.",range=60,last_day="4/10/20") 
```

This graph is interesting for a number of reasons.

We see that around 1st of March, the number of cases in South Korea was growing exponentially. Let us zoom in to see this better:


```{r, echo=FALSE}
one_region(what="cases",data=cases_global,region1="Korea, South",range=29, last_day="3/30/20") 
```
