---
title: "Coronavirus in Brazil"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size=1>

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv). The program that produces the plots is available as [report-Brazil.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Brazil.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details. (In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
</font>

```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

source("../src/covid-19_global.R")
```

<font size=3>

The current data of coronavirus deaths from Brazil is:

```{r, echo=FALSE}
one_region(what="deaths",data=deaths_global,region="Brazil",range = 120)
```


Zooming back into the past shows that when Brazil had its first 80 deaths on **March 27**, it looked to be on a similar trajectory as Italy 27 days earlier.

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Brazil",region2="Italy",last_day="3/27/20",lag=27)
```

But since then, Brazil has been on a flatter trajectory:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Brazil",region2="Italy",last_day="4/27/20",lag=44, range=40)
```


```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region2="Italy",region1="Brazil", lag=58, range=60)
```

Nevertheless, Brazil's new daily deaths are still growing.

</font>
