---
title: "Coronavirus Growth in the US States"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size="1"> 

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv).

The program that produces the plots below is available as [report-US-states.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-US-states.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)

</font> 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)

# Download raw data

deaths_df <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

last_column <- colnames(deaths_df)[ncol(deaths_df)]

# Select, rename, filter what is needed for the analysis

deaths_df %>%
  as_tibble() %>%
  select(-UID,-iso2,-iso3,-code3,-FIPS,-Country_Region,-Lat,-Long_,-Combined_Key) %>%
  rename(county=Admin2,state=Province_State,population=Population) %>%
  filter(!(county=="") & !(county=="Unassigned") & !grepl("Out of",county)) %>%
  mutate(population=as.numeric(population)) ->
deaths_tibble

deaths_tibble %>%
  pivot_longer(c(`1/22/20`:all_of(last_column)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  mutate(deaths_per_million = round(as.numeric(deaths)/population*1000000)) ->
deaths

# Make a table with populations of states

deaths_tibble %>%
  group_by(state) %>%
  summarise(state_pop = sum(population)) ->
state_populations

# Make a table with US population

state_populations %>%
  summarise(us_pop = sum(state_pop)) ->
us_population

# Make a table with states and deaths_per_million

deaths %>% 
  subset(date > as.Date("2020-03-15")) %>%
  subset(date < as.Date("2020-05-10")) %>%
  group_by(state,date) %>%
  summarise_at(vars(deaths),sum) %>%
  ungroup() %>%
  inner_join(state_populations, by = c("state" = "state")) %>%
  mutate(deaths_per_million = round(deaths/state_pop*1000000)) ->
state_deaths_per_million

# Make a table with all states sorted by deahts_per_million

state_deaths_per_million %>%
  arrange(desc(deaths_per_million)) %>%
  distinct(state) ->
states_by_deaths
```

<font size="3"> 

## May 5, 2020

We continue to see that New York has been slowing down the growth.

```{r, echo=FALSE}
state_deaths_per_million %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```


Let us zoom into the picture. We start with the states **ranked 1-5**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,1:5), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```

It looks as if these states got closer to a linear trajectory by now. 

Now let us look at **rank 6-10**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,6:10), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```


Here are the states **ranked 11-15**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,11:15), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```


Here are the states **ranked 16-20**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,16:20), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```


**Rank 21-25**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,21:25), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```

I find it interesting how close the states ranked 21-30 are to each other.

**Rank 26-30**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,26:30), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```


**Rank 31-40**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,31:40), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```

**Rank 41-50**:

```{r, echo=FALSE}
state_deaths_per_million %>%
  inner_join(slice(states_by_deaths,41:50), by = c("state" = "state")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = deaths_per_million, color = state))
```

</font>
