---
title: "Coronavirus New York vs Italy"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-New_York.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-New_York.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

cases_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"),check.names = FALSE)

deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

```{r, echo=FALSE}
source("../src/covid-19_US.R")
```


## March 12

New York, New York is a special case. On March 12, it still looks to be in a similar position to other European countries other than Italy. Just one death and a still small number of cases. The graph below gives an estimate of NY lagging 13 days behind Italy.

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="New York",province_state="New York",region2="Italy",last_day="3/12/20",range=11,lag=13) 
```


## March 19

But only a week later something weird has happened. The number of deaths is following the line predicted by the number of cases a week earlier:

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="New York",province_state="New York",region2="Italy",last_day="3/19/20",range=18,lag=13) 
```

But the number of cases is going through the roof:

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="New York",province_state="New York",region2="Italy",last_day="3/19/20",range=18,lag=13) 
```


## March 27

A week later, it is clear that the deaths in New York are growing much faster:

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="New York",province_state="New York",region2="Italy",last_day="3/27/20",range=26,lag=13) 
```

And, as worrying, the lag in the number of cases has totally disappeared:

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="New York",province_state="New York",region2="Italy",last_day="3/27/20",range=26,lag=0)
```


## April 2

Another week later, the lag has also disappeared in the number of deaths:

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="New York",province_state="New York",region2="Italy",last_day="4/2/20",lag=0)
```

And the number of cases keeps looking very bad indeed.

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="New York",province_state="New York",region2="Italy",last_day="4/2/20",lag=0)
```


## latest

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="New York",province_state="New York",region2="Italy",lag=0)
```


```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="New York",province_state="New York",region2="Italy",lag=0)
```


