---
title: "Coronavirus Sweden vs Norway"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Norway-Sweden.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Norway-Sweden.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

source("../src/covid-19_global.R")
```

## March 11

The lockdown in Norway came on March 12. 

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region2="Norway",region1="Sweden",last_day="3/11/20",range=12,lag=2)
```

## March 18

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Sweden",region2="Norway",last_day="3/18/20",range=18,lag=6) 
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Sweden",region2="Norway",last_day="3/18/20",range=18,lag=0) 
```

## March 25

As in other situations, one begins to see the lockdown in the data after approximately two weeks. 

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Sweden",region2="Norway",last_day="3/25/20",lag=10)
```


```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Sweden",region2="Norway",last_day="3/25/20",lag=0)
```

## latest

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Sweden",region2="Norway",lag=10,range=40)
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Sweden",region2="Norway",lag=0, range=40)
```
