---
title: "Coronavirus Netherlands vs Germany"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size=1>
We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv). The program that produces the plots is available as [report-Netherlands-Germany.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Netherlands-Germany.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details. (In Firefox, the links above may raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
</font>

```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

source("../src/covid-19_global.R")
```

<font size=3>

As of today the plots of the Netherlands and Germany look as follows:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Netherlands",region2="Germany",range=40)
```

It looks like both countries are currently on an approximately linear trajectory. Nevertheless there are more new deaths per day (relative to the total population) in the Netherlands than in Germany.

It is also interesting to zoom back to the time when most European countries decided to follow Italy and implement lockdown measures:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region2="Netherlands",region1="Germany",last_day="3/21/20",range=30,lag=6)
```

The data shows that on March 21, Germany was approximately a week behind the Netherlands with both countries being on an exponential trajectory. It would be interesting to understand how from this similar starting point the quite different developments shown in the first graph developed.

Finally, it is of interest to note that while the number of deaths develops differently in both countries, the number of cases align almost perfectly. My guess is that this discrepancy is due to the fact that Germany is testing much more than the Netherlands. Corrected by population, Germany is testing [almost 3x](https://www.statista.com/statistics/1109066/coronavirus-testing-in-europe-by-country/) as many people as the Netherlands.


```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Netherlands",region2="Germany",range=50,lag=0)
```

</font>
