---
title: "Coronavirus Korea, South vs US"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, echo=FALSE}
source("../src/covid-19_global.R")
```

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Korea, South-US.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Korea, South-US.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

## March 10

New York State lockdown on 22/March

California on 19/March



```{r, echo=FALSE}
one_region(what="deaths",data=deaths_global,region="US",last_day="",range=35)
```
 
```{r, echo=FALSE}
one_region(what="deaths",data=deaths_global,region="Korea, South",last_day="",range=65)
```


```{r, echo=FALSE}
two_regions(what="deaths",data=cases_global,region1="Korea, South",region2="US",last_day="",range=65,lag=0)
```



```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region2="Korea, South",region1="US",region2_pop = "Korea, Rep.",region1_pop="United States",last_day=,range=40,lag=0)
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Korea, South",region2="US",region1_pop="Korea, Rep.", region2_pop="United States",last_day=,range=60,lag=21)
```