---
title: "Covid-19 Orange County, CA"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size=1>
We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv). The program that produces the plots is available as [report-Orange.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Orange.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details. (In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
</font>

```{r, echo=FALSE}    
deaths_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

cases_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"),check.names = FALSE)

source("../src/covid-19_US.R")
```


```{r, echo=FALSE}
one_region(what="deaths",data=deaths_us,admin="Orange",province_state="California",range=110)
```

```{r, echo=FALSE}
one_region(what="cases",data=cases_us,admin="Orange",province_state="California",range=110)
```
