---
title: "Coronavirus Deaths in the World (May 5)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size=1>
We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv). The program that produces the plots is available as [report-world-deaths-2020-03-20.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-world-deaths-2020-03-20.Rmd). It can be downloaded and modified for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details. (In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
</font>

<font size=3>

```{r, echo=FALSE, message=FALSE, warning=FALSE}    

# To choose whether to plot deaths or cases search this file for "what"
# To choose which range of dates to plot search this file for "subset(date"

library(tidyverse)
library(lubridate)

# Loading and cleaning population data

read.csv(url("https://raw.githubusercontent.com/datasets/population/master/data/population.csv")) %>%
  as_tibble() %>%
  filter(Year == "2018") %>%
  select(-`Country.Code`,-`Year`) %>%
  rename(country = `Country.Name`, population = `Value`) %>%
  mutate(country = as.character(country)) %>%
  mutate(population = as.numeric(population)) %>%
  mutate(country = if_else(country=="United States", "US",country)) %>%
  mutate(country = if_else(country=="Korea, Rep.", "South Korea",country)) ->
populations

# Loading and cleaning deaths data. Making sure that all tables have the same country names.

read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"),check.names = FALSE) %>%
  as_tibble() %>%
  select(-Lat,-Long) %>%
  rename(state=`Province/State`,country = `Country/Region`) %>%
  filter(state=="") %>%
  mutate(country = as.character(country)) %>%
  mutate(country = if_else(country=="Korea, South", "South Korea",country)) %>%
  mutate(country = if_else(country=="Czechia", "Czech Republic",country)) %>%
  inner_join(populations, c=("country" = "country")) %>%
  select(population,everything()) %>%
  select(country,everything()) %>%
  select(-state) ->
deaths_tibble

deaths_tibble %>%
  pivot_longer(c(`1/22/20`:ncol(.)),names_to="date",values_to="deaths") %>%
  mutate(date=mdy(date)) %>%
  mutate(per_million = round(deaths/population*1000000)) ->
deaths

# Loading and cleaning cases data. Making sure that all tables have the same country names.

read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv")) %>%
  as_tibble() %>%
  select(-Lat,-Long) %>%
  rename(state=`Province/State`,country = `Country/Region`) %>%
  filter(state=="") %>%
  mutate(country = as.character(country)) %>%
  mutate(country = if_else(country=="Korea, South", "South Korea",country)) %>%
  mutate(country = if_else(country=="Czechia", "Czech Republic",country)) %>%
  inner_join(populations, c=("country" = "country")) %>%
  select(population,everything()) %>%
  select(country,everything()) %>%
  select(-state) ->
cases_tibble

cases_tibble %>%
  pivot_longer(c(`1/22/20`:ncol(.)),names_to="date",values_to="cases") %>%
  mutate(date=mdy(date)) %>%
  mutate(per_million = round(cases/population*1000000)) ->
cases
```


```{r, echo=FALSE}

# Choose what to plot: cases or deaths 

data <- deaths
# data <- cases

what <- "deaths"
# what <- "cases"
```

```{r, echo=FALSE}

# Select date range

data %>%
  subset(date > as.Date("2020-03-01")) %>%
  subset(date < as.Date("2020-05-05")) ->
data
```

```{r, echo=FALSE}

# Order countries by highest number of deaths

data %>%
  arrange(desc(per_million)) %>%
  distinct(country) ->
countries_sorted
```


#### Coronavirus deaths per million inhabitants on May 5, 2020

We list the countries with the most coronavirus cases per million inhabitants. Not listed are China, San Marino, Andorra, Luxembourg, Monaco, Antigua and Barbuda, Iceland, Liechtenstein and all countries that had less than 5 death per million at the time (according to the available data).


```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted,2,4,5,6,7,8), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted,9,10,11,12,14,15), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```


```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted,16:21), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted,22:27), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted,27:32), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted, 35,36,38:45), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted, 46:57), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

```{r, echo=FALSE}
data %>%
  inner_join(slice(countries_sorted, 58:75), by = c("country" = "country")) %>%
  ggplot() + geom_line(mapping = aes(x = date, y = per_million, color = country)) + labs(x="",y=paste(what,"per million"))
```

</font>
