---
title: "Coronavirus in Orange"
output: html_document
---

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Orange.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Orange.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

cases_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"),check.names = FALSE)

deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

```{r, echo=FALSE}
source("../src/covid-19_US.R")
```

## March 19

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Orange",province_state="California",region2="Italy",last_day="3/19/20",range=18,lag=20) 
```

## March 27

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Orange",province_state="California",region2="Italy",last_day="3/27/20",lag=20)
```


## April 2

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Orange",province_state="California",region2="Italy",last_day="4/2/20",lag=21)
```


```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Orange",province_state="California",region2="Italy",last_day="4/2/20",lag=26)
```

## latest

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Orange",province_state="California",region2="Italy",lag=22)
```


```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Orange",province_state="California",region2="Italy",lag=27)
```

