---
title: "Coronavirus Orange vs Italy"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Orange.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Orange.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_US.csv"),check.names = FALSE)

cases_us <- read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_US.csv"),check.names = FALSE)

deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

```{r, echo=FALSE}
source("../src/covid-19_US.R")
```

# Latest plots

It would be great if the growth in number of cases was slowing down already ... 

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Orange",province_state="California",region2="Italy",lag=30)
```

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Orange",province_state="California",region2="Italy",lag=25)
```

# April 3

```{r, echo=FALSE}
two_regions(what="deaths",data_global=deaths_global,data_us=deaths_us,admin2="Orange",province_state="California",region2="Italy",lag=27,last_day="4/3/20")
```

The graph shows that the number of deaths is doubling approximately every 3 days. This is very much the situation in which Italy was a month ago.

We can also compare the number of confirmed cases. This shows a similar pattern:

```{r, echo=FALSE}
two_regions(what="cases",data_global=cases_global,data_us=cases_us,admin2="Orange",province_state="California",region2="Italy",lag=22,last_day="4/3/20")
```

