---
title: "Coronavirus Poland vs Italy"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Poland.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Poland.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

source("../src/covid-19_global.R")
```


## latest

Poland is showing a slower growth than Italy and bigger lag than most other countries we looked at:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Poland",region2="Italy",lag=38)
```

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Poland",region2="Italy",lag=36
            )
```
