---
title: "Coronavirus Netherlands vs Germany"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

<font size=1>
We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv). The program that produces the plots is available as [report-Netherlands-Germany.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Netherlands-Germany.Rmd.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details. (In Firefox, the links above may raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
</font>

```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))

source("../src/covid-19_global.R")
```

<font size=3>

As of today the plots of the Netherlands and Germany look as follows:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Netherlands",region2="Germany",range=40)
```

Another way to visualise the difference between the two countries is to ask the following question. How many days ago did the Netherlands have as many cases as Germany has today (corrected for the different population sizes)? To find this out, we simply move the Dutch curve to the right until the top right corners match up:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Germany",region2="Netherlands",range=40,lag=18)
```

This shows us that at the moment where both countries had (relative to their population sizes) the same number of deaths, Germany was already in linear growth while the Netherlands was still in the exponential phase.

It is also interesting to zoom back to the time when most European countries decided to follow Italy and implement lockdown measures:

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region2="Netherlands",region1="Germany",last_day="3/21/20",range=30,lag=6)
```

The data shows that on March 21, Germany was approximately a week behind the Netherlands with both countries being on an exponential trajectory. As we have seen above, Germany was able to get out of the exponential growth. It would be interesting to correlate this with the corresponding policy measures.

Finally, it is of interest to note that while the number of deaths develops differently in both countries, the number of cases align almost perfectly. My guess is that this is due to the fact that Germany is testing much more as the Netherlands. Corrected by population, Germany is testing [almost 3x](https://www.statista.com/statistics/1109066/coronavirus-testing-in-europe-by-country/) as many people than the Netherlands.


```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Netherlands",region2="Germany",range=50,lag=0)
```

</font>
