---
title: "Coronavirus in Austria"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r, echo=FALSE}
source("../src/covid-19_global.R")
```

We use the data from Johns Hopkins University about [global deaths](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv)  and [global confirmed cases](https://github.com/CSSEGISandData/COVID-19/blob/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv).

The program that produces the plots is available as [report-Austria.Rmd](https://github.com/alexhkurz/coronavirus-in-R/blob/master/reports/report-Austria.Rmd). It is easy to download the program and to modify the relevant parameters for your own experiments, see the [README](https://github.com/alexhkurz/coronavirus-in-R/) for more details.

(In Firefox, the links above raise a "Blocked by Content Security Policy", but can be opened with "Open Link in New Tab".)
    
```{r, echo=FALSE}    
deaths_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))

cases_global <- read.csv(check.names = FALSE,url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv"))
```

## March 12

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Austria",region2="Italy",last_day="3/12/20",range=12,lag=10)
```

## March 15

[As of 16 March](https://en.wikipedia.org/wiki/2020_coronavirus_pandemic_in_Austria), nationwide, homes may only be left for one of the following reasons:[30]
- necessary professional activities
- necessary purchases (groceries or medication)
- assisting other people
- activities outside, alone or in the company of people living in the same household.

On this day there was still only one dead, with the number of cases as follows:

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Austria",region2="Italy",last_day="3/15/20",range=14,lag=8) 
```

## March 26

On 27 March, Federal Minister of Health Rudolf Anschober announced that, in Austria, the peak of the pandemic is expected to be between mid of April and mid of May 2020. On this day, the situation was as follows:

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Austria",region2="Italy",last_day="3/26/20",lag=6)
```


```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Austria",region2="Italy",last_day="3/26/20",lag=18)
```

On 30 March, the Austrian government announced that everyone entering a store has to wear a face mask effective 6 April.

## April 2

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Austria",region2="Italy",last_day="4/2/20",lag=7)
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Austria",region2="Italy",last_day="4/2/20",lag=20)
```

## latest

While on March 26, the Austrian and Italian curves could still be aligned, the recent data shows that in Austria the curve flattened more quickly.

```{r, echo=FALSE}
two_regions(what="cases",data=cases_global,region1="Austria",region2="Italy",lag=12)
```

```{r, echo=FALSE}
two_regions(what="deaths",data=deaths_global,region1="Austria",region2="Italy",lag=24)
```
