---
output: rmarkdown::github_document
---

# How many days does Germany lag behind Italy?

**Lesson 2:**

- This lesson is best read by loading [lesson-02.Rmd](lesson-02.Rmd) into Rstudio because the code can be run inside the Rmd-file.
- On the other hand, the typesetting is better in [lesson-02.md](lesson-02.md), the latter being automatically produced from lesson-01.Rmd using the Knit feature of Rstudio.
- The aim of this lesson is the short program [lesson-02.R](lesson-02.R).

## Idea

(Written March 22, 2020.)

There is a discussion now why Germany has many fewer deaths than Italy. In fact, writing March 22, according to [worldometers](https://www.worldometers.info/coronavirus/#countries), Italy has 60k cases and 5.5k deaths, whereas Germany has 25k cases and 0.1k deaths. That is, Italy has a case fatality rate of 9% and Germany of 0.4%. What is going on here? 

Could it be that this is just due to different testing regimes? 

Here is a simple analysis. The idea is to see what happens if we ignore tests (that is, ignore the number of total cases) and only look at the number of confirmed deaths. Can we then see any difference between Germany and Italy when we take into account that Germany lags behind Italy? 

We ask the question whether the data is consistent with the **hypothesis** that Germany and Italy follow the same development, only separated by a certain time lag. We **estimate** the time lag by moving the Italian curve so that it best matches the German curve.

On March 22, this produced [this graph](https://github.com/alexhkurz/coronavirus-in-R/blob/master/plots/2020-03-22/Germany-Italy-March-22.png), overlaying deaths in Italy in red and deaths in Germany in blue. The German curve starts 13 days ago when the first deaths appeared and the Italian curve starts 32 days ago. Italian numbers are multiplied by 1.32 to account for the difference in population sizes. 

If you run the program on more recent data you will get a different result. It will be interesting to compare.

## Implementation

Estimate how many days Germany lags behind Italy by overlaying the number of deaths in each country.

The lag between the two countries is computed as `italy_first - germany_first`.

`germany_first` is the number of days ago from which we want to start plotting the data. It could be chosen as the first day of a recorded coronavirus death in Germany' or just as 30 days ago, or as the number of days that have passed in the current month or any other number of days that interests you.

`italy_first` should be the corresponding number of days which produces the best match of the two curves. At the time of writing this was approximately `germany_first+19`.

Note: The results of the analysis change when Johns Hopkins update their data. One may want to adapt the program accordingly by changing the variables `germany_first` and `italy_first`.

## Download the data

Download the current data from Johns Hopkins
```{r}
mydata = read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
```
Show the last date for which there is data (recall the function `ncol()` from the first lesson):
```{r}
View(colnames(mydata)[ncol(mydata)]) 
```
Get the indides of the rows for Germany and Italy:
```{r}
germany <- 121       
italy <- 138
```
`range` is the width of the window (number of days -1)
```{r}
range <- 15           # last-day - first_day
germany_first <- 15   # how many days ago? first German death on March 8
italy_first <- 35     # how many days ago?
```
We need to correct for the fact that the German population is bigger than the Italian one.
```{r}
population_ratio_germany_italy <- 1.38
```
The next four lines are (almost) the same as in Lesson 1
```{r}
german_deaths <- mydata[germany,(ncol(mydata)-germany_first):(ncol(mydata)-germany_first+range)]
german_deaths <- gsub(",", "", german_deaths)                     
german_deaths <- as.numeric(german_deaths)                      
```
And now we repeat the same for Italian data
```{r}
italian_deaths <- mydata[italy,(ncol(mydata)-italy_first):(ncol(mydata)-italy_first+range)]
italian_deaths <- gsub(",", "", italian_deaths)                   
italian_deaths <- as.numeric(italian_deaths)
```
One last twist: We do not use the function `plot()` draw German data and then use the function `lines()` to draw the Italian data in the German plot:
```{r}
plot(german_deaths, col="black", main="German (black), Italy (red)", xlab="days", ylab="German deaths")   
lines(population_ratio_germany_italy*italian_deaths, col="red")   # plot Italy in the same window
```


## Suggested Exercises

(Time for some music? I wrote this listening to [Interstellar Space](https://www.youtube.com/watch?v=RyIPmmCmIb0&list=PLSeOx7nxhymJl1aXmMDM3-TyiLodxcavz).)

- If the graphs do not match, play around with the variable `italy_first` and try to find the best match. The difference between `germany_first` and `italy_first` is the new lag.

- Copy and paste the code and adapt the program so that it compares a country of your choice to Italy.

  - The copied code should appear under the Germany-Italy plot.
  - Find a country. Remember the number of its row.
  - In the copied code
    - replace `germany` by `name_of_new_country`
    - run your code 
    - watch out for error messages
    - one error is likely to be `object `name_of_new_country` ... a good place to define the variable `name_of_new_country` is after the lines defining `germany` and `italy`

  - Don't forget to put in the correct ratio of the new country's versus Italian's population.

  - Estimate the lag between the two countries by finding the best fit for the two curves by changing the value of `italy_first`.
  
  - Adapt the labelling of the plot to fit the new country.
  
- Repeat with some other countries. Here are some I would find interesting: Brazil, South Korea, Japan, France, Spain, US, UK, Australia, etc



