---
title: How many days does Germany lag behind Italy?
---

Estimate how many days Germany lags behind Italy by overlaying the number of deaths in each country.
The lag between the two countries is computed as italy_first - germany_first.
`germany_first` can be chosen as the first day of a recorded coronavirus death in Germany.
`italy_first` is the corresponding day which produce the best match of the two curves. 

Note: The results of the analysis change when Johns Hopkins update their data.
One may want to adapt the program accordingly by increasing by one the variables

  germany_first, italy_first

Sownload the current data from Johns Hopkins

```{r}
mydata = read.csv(url("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_deaths_global.csv"))
View(mydata)
```

Show the last date for which there is data

```{r}
View(colnames(mydata)[ncol(mydata)]) 
```

# get the number of the rows for different countries
#
```{r}
germany <- 121       
italy <- 138
```

Germany vs Italy
32-13=19 day lag estimated on March 22: range=13, germany_first=13,italy_germany_first=32
35-15=20 day lag estimated on March 24: range=15, germany_first=15,italy_germany_first=35

```{r}
range <- 15           # last-day - first_day
germany_first <- 15   # how many days ago? first German death on March 8
italy_first <- 35     # how many days ago?
population_ratio_germany_italy <- 1.38

german_deaths <- mydata[germany,(ncol(mydata)-germany_first):(ncol(mydata)-germany_first+range)]
german_deaths <- gsub(",", "", german_deaths)                     
german_deaths <- as.numeric(german_deaths)                      
plot(german_deaths, col="black", main="German (black), Italy (red)", xlab="days", ylab="German deaths")   

italian_deaths <- mydata[italy,(ncol(mydata)-italy_first):(ncol(mydata)-italy_germany_first+range)]
#View(mydata[italy,1:2])       # Verify country
italian_deaths <- gsub(",", "", italian_deaths)                   
italian_deaths <- as.numeric(italian_deaths)                      
lines(population_ratio_germany_italy*italian_deaths, col="red")   # plot Italy in the same window
```
