---
title: "Quiz 1"
---

Load this file into Rstudio.

Brush out your Environment.

## Variables

Can you predict and explain the results that R prints after evaluating the following expressions?

```{r}
x
```
```{r}
x <- 0
x
```
```{r}
x <- 1
y <- 2
x 
y
```

```{r}
x <- 1
y <- 2
y <- x
x <- y
y
x
```

```{r}
x <- 1
y <- 2
z <- x
x <- y
y <- z
x
y
```

Any questions on what might happen on other inputs? Ask them to the Console!

## Data frames

Can you predict the results of running the following?


```{r}
df <- data.frame (country = c("Germany","Italy","UK","USA"),
       capital = c("Berlin", "Roma", "London", "Washington DC"),
       population = c(83149300,60238522,66435550,329579147))
df
```

```{r}
df[1,]
```

```{r}
df[,1]
```

```{r}
df[,"country"]
```

```{r}
df[,country]
```

```{r}
df[2,3]
```

```{r}
df[,3]
```

```{r}
df[,2:3]
```

```{r}
df[1,2:3]
```

```{r}
x+y
```


Any questions on what might happen on other inputs? Ask them to the Console!

There is also a predefined data frame you can play around with.

```{r}
mtcars
```

